% Paste into Overleaf: replace \appendix … \end{document}
% (Includes STEP 9 table fix)

\appendix

\section{Appendix}

This appendix records the materials and prompt wording needed to reproduce the
audit. Each model call is a single independent evaluation: one listing, one
synthetic applicant, one JSON accept/reject reply.

\subsection{Turin Listings and National Backgrounds}
Five real two-room flats from \code{immobiliare.it} (June 2026) span Turin
rent levels from \eur500 to \eur1{,}750 per month. Every listing is crossed
with all 480 profiles in the main study.

\begin{table}[h]
\centering
\caption{Apartment stimuli used in the factorial audit.}
\label{tab:app-listings}
\small
\begin{tabular}{@{}llrr@{}}
\toprule
\textbf{ID} & \textbf{Neighbourhood} & \textbf{Rent} & \textbf{Size} \\
\midrule
A1 & Barriera di Milano      & \eur500   & 50\,m$^2$ \\
A2 & Centro                  & \eur1{,}750 & 49\,m$^2$ \\
A3 & Vanchiglia              & \eur890   & 60\,m$^2$ \\
A4 & San Paolo / Cenisia     & \eur650   & 43\,m$^2$ \\
A5 & Santa Rita              & \eur700   & 50\,m$^2$ \\
\bottomrule
\end{tabular}
\end{table}

National background is a categorical label shown verbatim to the model:
\emph{local citizen} (Italian, born in Italy); \emph{EU foreigner}; \emph{non-EU
foreigner} with a valid residency permit; \emph{refugee / asylum-seeker} with
international protection; and \emph{second-generation immigrant} (born in Italy
to immigrant parents). Gender is binary (male/female); income is low
(\eur12{,}000), medium (\eur28{,}000), or high (\eur60{,}000) per year.

\subsection{Synthetic Profile Design}
Profiles follow a fully crossed legitimate-factor design. There are
$24$ profile sets---all combinations of income, employment (employed vs.\
unemployed), marital status (single vs.\ married), and children (none vs.\ one
child). Each set contains $20$ applicants: $2$ genders $\times$ $5$ national
backgrounds $\times$ $2$ name replicates. Set IDs encode the four factors
(e.g.\ \code{S11\_memn} = medium income, employed, married, no children).

\paragraph{Example profile.}
\code{S14\_musy\_refugee\_male\_1}: medium income (\eur28{,}000), unemployed,
single parent with one child, male, refugee/asylum-seeker. This set is among the
hardest to approve because income is only moderate, employment is unstable, and
the flat is a one-bedroom unit.

\subsection{Prompt Templates and Model Output}
All conditions ask the model to act as a landlord's assistant in Turin. The
prompt lists the rental announcement (title, description, price, size, bedrooms,
neighbourhood, furnished flag) and the houseseeker profile (gender, national
background label, income, employment, marital status, children). The model
must answer with JSON only:
\code{\{"fit": "Yes"|"No", "motivation": "1--2 sentence reason"\}}.
No markdown or free text is permitted outside the JSON object on the main audit.

\paragraph{Baseline (main experiment and RQ4 control).}
The template above, with no fairness or reasoning instruction beyond the JSON
constraint.

\paragraph{Explicit fairness (RQ4).}
Same listing and profile block, prefixed with an instruction to base the
decision only on financial and housing-relevant factors and \emph{not} on gender,
ethnicity, national origin, immigration, or refugee status.

\paragraph{Chain-of-thought (RQ4).}
Same block, with internal three-step reasoning (financial qualifications,
housing fit, final decision) before returning the JSON answer; demographics must
not enter the reasoning.

\subsection{RQ4 Mitigation Results}
Table~\ref{tab:app-mitigation} summarises the paired mitigation study: the same
500 listing--profile pairs per model under baseline, explicit-fairness, and
chain-of-thought prompts. Neither variant removes the nationality gap; on
\code{owl-alpha}, chain-of-thought mainly lowers overall strictness
($-12.6$\,pp vs.\ baseline).

\begin{table}[h]
\centering
\caption{RQ4 mitigation summary ($n=500$ matched pairs per condition).}
\label{tab:app-mitigation}
\small
\setlength{\tabcolsep}{4pt}
\begin{tabular}{@{}lrrr@{}}
\toprule
\textbf{Condition} & \textbf{owl} & \textbf{qwen} & \textbf{$\Delta$} \\
\midrule
Baseline     & 37.6\% & 32.0\% & ref. \\
Fairness     & 37.4\% & 39.0\% & $-0.2$\,pp \\
CoT          & 25.0\% & 32.4\% & $-12.6$\,pp \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Reproducibility}
Code, JSON results, listing text, all 480 profiles, and an interactive dashboard
are available at \url{https://github.com/Sam9875/Tenant-bias-LLM}. The main
audit used \code{scripts/run\_sft.py}; RQ4 used
\code{scripts/mitigation\_experiment.py}. Total API volume: 7{,}800 single-call
evaluations (2{,}400 factorial rows and 1{,}500 mitigation rows per model).

\end{document}